---
title: "Dataset Proposal"
author: "Vikas Rayala, Manikanta Reddy Kallam"
date: "2023-04-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE}
library(pacman)
pacman::p_load(funModeling)
```

## [**Dataset Source and links:**]{.underline}

**Dataset description :** House price prediction based on locality and neighbor cities.

**File name:** California_Houses.csv

**Source :** The original data (without the distance features) was initially featured in the paper: Pace, R. Kelley, and Ronald Barry. "Sparse spatial autoregressions." Statistics & Probability Letters 33.3 (1997): 291-297. They collected information on the variables using all the block groups in California from the 1990 Cens us

**Link :** <https://www.kaggle.com/datasets/fedesoriano/california-housing-prices-data-extra-features?resource=download>

## [**Column level description and statistical analysis:**]{.underline}

```{r,echo=FALSE}
project_df <- read.csv("data/California_Houses.csv")
metadata <- funModeling::df_status(project_df, print_results = FALSE)
knitr::kable(metadata)
```

**Response Variable :**

1.  Median_House_Value : Median house value for households within a block (measured in US Dollars) [\$]

**Potential Predictor variables :**

1.  **Median_Income :**Median income for households within a block of houses (measured in tens of thousands of US Dollars) [10k\$]
2.  **Median_Age :** Median age of a house within a block; a lower number is a newer building [years]
3.  **Total_Rooms :** Total number of rooms within a block
4.  **Total_Bedrooms :** Total number of bedrooms within a block
5.  **Population :** Total number of people residing within a block
6.  **Households :** Total number of households, a group of people residing within a home unit, for a block
7.  **Latitude :** A measure of how far north a house is; a higher value is farther north [°]
8.  **Longitude :** A measure of how far west a house is; a higher value is farther west [°]
9.  **Distance_to_coast :** Distance to the nearest coast point [m]
10. **Distance_to_Los Angeles :** Distance to the centre of Los Angeles [m]
11. **Distance_to_San Diego :** Distance to the centre of San Diego [m]
12. **Distance_to_SanJose :** Distance to the centre of San Jose [m]
13. **Distance_to_SanFrancisco :** Distance to the centre of San Francisco [m]

## [Conclusion:]{.underline}

From the above table, we can see there are no missing values for any of the variables. So There is no need of data preprocessing and we can move ahead with analysis and data modelling.
